---
title: "Analyses of Lexicon+GPT Two-Stage Approach"
output: html_document
date: "2026-03-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(glmmTMB)
library(broom.mixed)
source('helper_functions.R')
maps_predict_colors = c('darkred', '#00BFC4')

gpt = read.csv('/Volumes/AUERBACHLAB/Columbia/MAPS_Language/scripts/maps_suicide_lexicon/model_outputs_step2/gpt/fewshot_window_v2/results/fwhm_1hr_focal_maps_inputs_for_llm_with_ids_with_responses.csv')

# Vector of binary column names
binary_cols = c(
  "jokes_hyperbole", "first_si_passive", "first_si_active",
  "first_nssi_thought", "first_nssi_behav", "first_si_absence",
  "first_victim", "first_sb", "first_lifehate", "first_helpseek",
  "first_reason_living", "second_support", "second_victim", "second_si",
  "second_sb", "second_nssi", "third_support", "third_victim", "third_si",
  "third_sb", "third_nssi", "gaming", "lethal_means", "resources",
  "maps", "celeb", "media", "art", "unclear", "other"
)


# Make sure binary columns are binarized
gpt[binary_cols] <- lapply(gpt[binary_cols], function(x) {
  x[x == "" | is.na(x)] <- 0      # Convert NA or blank string to 0
  as.numeric(x)                  # Convert to numeric if not already
})


gpt = mutate(gpt, timing = tolower(timing))


gpt = mutate(gpt,
                        current_first_person = case_when(
                          first_si_active == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_si_active == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          first_sb == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_sb == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          first_helpseek == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_helpseek == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          TRUE ~ 'No'
                        ))

gpt = mutate(gpt, response = label)

gpt = mutate(gpt, current_first_person = ifelse(current_first_person == 'Yes', 1, 0))

gpt = mutate(gpt, response = ifelse(response == 'Yes', 1, 0))

table(gpt$current_first_person)
table(gpt$response)
```

# First, see how well GPT-4o mini did in identifying current, first-person, authentic suicide-related language

```{r}
f = evaluate_predictions(input_df =  gpt, reference_col = 'current_first_person', prediction_cols = c('response'))

false_positives = dplyr::filter(gpt, current_first_person ==0 & response == 1)

false_negatives = dplyr::filter(gpt, current_first_person ==1 & response == 0)


false_positive_jokes = false_positives %>% 
  dplyr::filter(jokes_hyperbole == 1)

false_positive_passive = false_positives %>% 
  dplyr::filter(first_si_passive == 1)

false_positive_not_suicide = false_positives %>% 
  dplyr::filter(suicide_related == 0)

true_positives = dplyr::filter(gpt, current_first_person == 1)
```


# How strongly are the entries flagged by this Lexicon+GPT approach associated with STB history and baseline suicidal ideation?

```{r}
maps_selfreport = read_csv('/Volumes/AUERBACHLAB/Columbia/MAPS_Data/Analysis/Wrangling/Self_Report/data/selfreport_07.11.2024.csv') %>% 
  dplyr::select(ID, age, GROUP, Control, SSI19_i) 

load('../data_stage2/maps_full_codings_spellchecked.rda')

maps = mutate(final_spellcheck_codings, flag_bin = flag_final_no_emojis)
rm(final_spellcheck_codings)
gc()

maps = maps %>%
  distinct(text_clean, tm_message_start, tm_message_end, id_app, .keep_all = TRUE)

maps = left_join(maps %>% dplyr::select(ID=id, everything()), maps_selfreport, by = 'ID')

maps = maps %>%
  group_by(ID)%>%
  mutate(total_message = n()) %>%
  ungroup()

maps = left_join(maps, gpt %>% dplyr::select(ID = id, response, id_row, id_message, corrected_message, flagged), by = c('ID', 'id_row', 'id_message', 'corrected_message', 'flagged'))

maps = mutate(maps, gpt = ifelse(is.na(response), 0, response))
```

```{r}
by_id_summary = maps %>%
  group_by(ID)%>%
  summarise(total_message = n(),
            total_flagged = sum(flag_bin==1),
            proportion_flagged = total_flagged/total_message)

maps = maps %>%
  group_by(ID)%>%
  mutate(total_message = n()) %>%
  ungroup()



# remove participants with fewer than 1000 entries
maps = dplyr::filter(maps, total_message >= 1000)
gc()


maps = mutate(maps, lifetime_stb = ifelse(Control==0, 1, 0),
              suicide_related = ifelse(is.na(suicide_related), 0, suicide_related))
```


```{r}
maps = mutate(maps, timing = tolower(timing))


# Code key content categories as model outcomes
maps = mutate(maps,
                        current_first_person = case_when(
                          first_si_active == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_si_active == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          first_sb == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_sb == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          first_helpseek == 1 & 
                            grepl('current', timing)  ~ 'Yes',
                          first_helpseek == 1 & 
                            grepl('future', timing)  ~ 'Yes',
                          TRUE ~ 'No'
                        ),
              currfirst = ifelse(current_first_person=='Yes', 1, 0),
              jokes_hyperbole = ifelse(jokes_hyperbole=='1', 1, 0),
              jokes_hyperbole = ifelse(is.na(jokes_hyperbole), 0, jokes_hyperbole),
              first = case_when(
                first_si_passive==1 | first_si_active == 1 | first_nssi_thought == 1 |
                first_nssi_behav == 1 | first_si_absence ==1 | first_victim == 1 |
                first_sb ==1 | first_lifehate == 1 | first_helpseek ==1 | 
                first_reason_living == 1 ~ 1,
              TRUE ~ 0
              ),
              second = case_when(second_support ==1 | second_victim ==1 |
                                 second_si ==1 | second_sb == 1 | 
                                 second_nssi ==1 ~ 1,
              TRUE ~ 0),
              third = case_when(third_support ==1 | third_victim ==1 |
                                 third_si ==1 | third_sb == 1 | 
                                 third_nssi ==1 ~ 1,
                                TRUE ~ 0),
              false_positive = case_when(
                flag_bin ==1 & suicide_related == 0 ~ 1,
                TRUE ~ 0
              ),
              support = case_when(second_support ==1 | third_support == 1 ~1, 
                                  TRUE ~ 0))

table(maps$currfirst)
table(maps$jokes_hyperbole)

maps = mutate(maps, gpt_label = gpt)
```

# Make sure not to include any excluded MAPS participants
```{r}
maps_inclusion = read_csv('/Volumes/AUERBACHLAB/Columbia/MAPS_Data/Analysis/ID_FINAL/id_list_compiled_2026-02-10.csv')


maps_include_ids = maps_inclusion %>%
  dplyr::filter(!is.na(study_id), !grepl('ineligible', notes_main_idlist), !grepl('not eligible', notes_main_idlist))


removed_ids = dplyr::filter(maps, !ID %in% maps_include_ids$study_id)

maps = dplyr::filter(maps, ID %in% maps_include_ids$study_id)
```

```{r}
# Function for bootstrapping models and comparing strength of lexicon vs lexicon+GPT within bootstrap folds
# Saves odds ratio for each model out
one_bootstrap_gpt = function(seed, df){
  set.seed(seed)

  # get bootstrap sample using custom sample_participants() function
  boot_sample =  
    dplyr::select(df, ID, age, SSI19_i, flag_bin, gpt_label, lifetime_stb)
  boot_sample = sample_participants_optimized(boot_sample)
  boot_sample = mutate(boot_sample, ID = as.character(ID))
  
  
  boot_sample =  
    boot_sample %>%
    na.omit() %>% 
    mutate(SSI19_i = scale(SSI19_i))
  
  n_participants = length(unique(boot_sample$ID))


  # SI
  si_z_lexicon = glmmTMB(
    flag_bin ~ SSI19_i + age + (1 | ID),
    family = binomial(link = "logit"),
    data = boot_sample)
  
  si_z_gpt = glmmTMB(
    gpt_label ~ SSI19_i + age + (1 | ID),
    family = binomial(link = "logit"),
    data = boot_sample)
  
  or_si_lexicon = broom.mixed::tidy(si_z_lexicon, conf.int=TRUE, exponentiate=TRUE) %>% 
    mutate(coding = 'lexicon')
  or_si_gpt = broom.mixed::tidy(si_z_gpt, conf.int=TRUE, exponentiate=TRUE) %>% 
    mutate(coding = 'gpt')
  
  # STB
  stb_lexicon = glmmTMB(
    flag_bin ~ lifetime_stb + age + (1 | ID),
    family = binomial(link = "logit"),
    data= boot_sample)
  
  stb_z_gpt = glmmTMB(
    gpt_label ~ lifetime_stb + age + (1 | ID),
    family = binomial(link = "logit"),
    data = boot_sample)
  
  or_stb_lexicon = broom.mixed::tidy(stb_lexicon, conf.int=TRUE, exponentiate=TRUE) %>% 
    mutate(coding = 'lexicon')
  or_stb_gpt = broom.mixed::tidy(stb_z_gpt, conf.int=TRUE, exponentiate=TRUE) %>% 
    mutate(coding = 'gpt')
  
  or_table = rbind(or_si_lexicon, or_si_gpt, or_stb_lexicon, or_stb_gpt) %>%
    mutate(iter = seed, n_participants = n_participants)
  
  
  return(or_table)

}
```

# Bootstrapping in MAPS 
```{r}
n_iter = 100

start_time = Sys.time()
for (i in 1:n_iter){
  print(i)
  boot_tmp=one_bootstrap_gpt(seed=i, df = maps)
  if(i == 1){
    boot_output = boot_tmp
    }
  else{
      boot_output = rbind(boot_output, boot_tmp)
  }
  end_time = Sys.time()
  print(end_time - start_time)
  time_elapsed = end_time - start_time  
  save(boot_output, time_elapsed, file = '../model_outputs_step2/bootstrap_outputs_gpt_vs_lexicon_maps.rda')
}

```

# Non-bootstrapped MAPS analysis

```{r}
outcome_variables = c('flag_bin', 'suicide_related', 'currfirst', 'gpt')
```


# Model the content conglomerate category outcomes (e.g., `outcome_variables`)
```{r}
maps_long = maps %>%
  dplyr::select(ID, age, SSI19_i, lifetime_stb, all_of(outcome_variables)) %>%
  mutate(SSI19_i_z = scale(SSI19_i)) %>%
  pivot_longer(cols = all_of(outcome_variables))


maps_nest = maps_long %>%
  group_by(name) %>%
  nest()


maps_si_z_models = maps_nest %>%
  mutate(model = purrr::map(data, ~glmmTMB(data = ., value ~ SSI19_i_z + age + (1|ID), 
                                           family = binomial(link = 'logit'))),
         coef = purrr::map(model, ~broom.mixed::tidy(., conf.int=TRUE))
  )

maps_stb_models = maps_nest %>%
  mutate(model = purrr::map(data, ~glmmTMB(data = ., value ~ lifetime_stb + age + (1|ID), 
                                           family = binomial(link = 'logit'))),
         coef = purrr::map(model, ~broom.mixed::tidy(., conf.int=TRUE, exponentiate=TRUE))
  )


maps_si_z_coef = maps_si_z_models %>% unnest(coef) %>%
  dplyr::select(-model, -data) %>%
  dplyr::filter(term == 'SSI19_i_z')

maps_stb_or = maps_stb_models %>% unnest(coef) %>%
  dplyr::select(-model, -data) %>%
  dplyr::filter(term == 'lifetime_stb')
```


```{r}
save(maps_si_z_models, maps_stb_models, file = '../model_outputs_step2/nobootstrap_outputs_gpt_vs_lexicon_maps.rda')
```

```{r}
maps_si_z_coef <- mutate(maps_si_z_coef, 
                      name_recode = dplyr::recode(name,
                                                  flag_bin = 'Flagged By Lexicon',
                                                  suicide_related = 'Lexicon + True Positive (Human-Coded)',
                                                  false_positive = 'False Positive',
                                                  jokes_hyperbole = 'Jokes/Hyperbole',
                                                  currfirst = 'Lexicon + Current, 1st Person\n& Authentic (Human-coded)',
                                                  first = '1st-person',
                                                  second = '2nd-person',
                                                  third = '3rd-person',
                                                  support = 'Supporting Other',
                                                  gpt = 'Lexicon + GPT4'),
                      lex = case_when(name=='flag_bin' ~ 'Flagged By Lexicon', 
                                      name == 'gpt' ~ 'Flagged by Lexicon + GPT',
                                      TRUE ~ 'Flagged By Lexicon\n+ Human Coding'))

maps_stb_or <- mutate(maps_stb_or, 
                      name_recode = dplyr::recode(name,
                                                  flag_bin = 'Flagged By Lexicon',
                                                  suicide_related = 'Lexicon + True Positive (Human-Coded)',
                                                  false_positive = 'False Positive',
                                                  jokes_hyperbole = 'Jokes/Hyperbole',
                                                  currfirst = 'Lexicon + Current, 1st Person\n& Authentic (Human-coded)',
                                                  first = '1st-person',
                                                  second = '2nd-person',
                                                  third = '3rd-person',
                                                  support = 'Supporting Other',
                                                  gpt = 'Lexicon + GPT4'),
                      lex = case_when(name=='flag_bin' ~ 'Flagged By Lexicon', 
                                      name == 'gpt' ~ 'Flagged by Lexicon + GPT',
                                      TRUE ~ 'Flagged By Lexicon\n+ Human Coding'))

maps_stb_or %>% dplyr::select(name, estimate, conf.low, conf.high)
maps_si_z_coef %>% dplyr::select(name, estimate, conf.low, conf.high)

```


# Load PREDICT
```{r}
gpt_predict = read_csv('/Volumes/AUERBACHLAB/Columbia/MAPS_Language/scripts/maps_suicide_lexicon/model_outputs_step2/gpt/fewshot_window_predict_v2/results/fewshot_predict_v2_results.csv')


gpt_predict = mutate(gpt_predict, entry_id = as.numeric(sub("request_id-(\\d+)_.*", "\\1", custom_id)))
gpt_predict = mutate(gpt_predict, ID = sub(".*_(\\d{4})\\.csv$", "\\1", custom_id))

gpt_predict = dplyr::select(gpt_predict, ID, entry_id, label, reasoning)

predict_full = read_csv('../data_stage2/predict_flagged_vs_maps_final_2025-08-11_with_id.csv')

predict_unique_id = data.frame(filepath=unique(predict_full$filepath))
predict_unique_id = mutate(predict_unique_id, ID = str_extract(filepath, "(?<=PREDICT/)[^/]+"))

predict_full = left_join(predict_full, predict_unique_id, by = 'filepath')


predict = left_join(predict_full, gpt_predict, by = c('ID', 'entry_id'))



predict = mutate(predict, gpt_label = ifelse(label == 'Yes', 1, 0),
                 gpt_label = ifelse(is.na(gpt_label), 0, gpt_label))


```

## prep for predict gpt analysis

```{r}
load('/Volumes/AUERBACHLAB/Columbia/SP_Data/Analysis/Wrangling/Self_Report/predict_demo_01.05.26.Rda')

predict_stb = df %>%
  dplyr::select(., 
                ID, gender, orientation, cis, cishet, age, 
                contains('cssrs'),
                group,
                contains('ssi')) %>%
  mutate(lifetime_stb = ifelse(
    cssrsLifetimeMostSevere > 2 | cssrsLifetimeAttempt ==1 |
    cssrsPast2moMostSevere > 2, 1, 0),
    lifetime_stb = ifelse(
     is.na(lifetime_stb) & SSI21_total_i == 0, 0, lifetime_stb
    ),
    stb_group = case_when(
      lifetime_stb ==1 ~ 'Lifetime STB',
      lifetime_stb ==0 & (group=='MDD' | group=='remMDD') ~ 'Lifetime MDD',
      lifetime_stb ==0 & group=='HC' ~ 'HC',
    ),
    recent_active_ideation = ifelse(cssrsPast2moMostSevere > 2, 1, 0)
  ) %>%
  dplyr::select(-contains('cssrs'))

predict = dplyr::select(predict,
                            -contains('suicide'),
                            -cat_tz,
                            -contains('emoji'))

predict_stb_nona = predict_stb %>% dplyr::filter(!is.na(lifetime_stb)) 

predict_stb_nona %>%
  group_by(lifetime_stb) %>%
  summarise(pct = n()/nrow(predict_stb_nona))

predict_stb_nona %>%
  group_by(recent_active_ideation) %>%
  summarise(pct = n()/nrow(predict_stb_nona))

table(predict_stb_nona$group) / nrow(predict_stb_nona)


predict = left_join(predict, predict_stb, by = 'ID')

predict_n_entries = predict %>%
  mutate(date = as.Date(tm_message_start)) %>%
  group_by(ID, lifetime_stb, date) %>%
  summarise(n_entries = n()) %>%
  mutate(cohort = 'PREDICT')


by_id_summary_predict = predict %>%
  group_by(ID)%>%
  summarise(total_message = n(),
            total_flagged = sum(flag_bin==1),
            proportion_flagged = total_flagged/total_message)

# what proportion of predict participants have any flagged?
dplyr::filter(by_id_summary_predict, total_flagged > 0) %>% nrow() / nrow(by_id_summary_predict)

gc()

```


```{r}
predict = predict %>%
  group_by(ID)%>%
  mutate(total_message = n()) %>%
  ungroup()

# filter out predict participants with under 1000 entries
predict = dplyr::filter(predict, total_message >= 1000)


predict_for_analysis = dplyr::filter(predict, !is.na(lifetime_stb))
```

# Non-bootstrapped PREDICT analysis

```{r}
outcome_variables_predict = c('flag_bin', 'gpt_label')

```


# Model the content conglomerate category outcomes (e.g., `outcome_variables`)
```{r}
predict_long = predict_for_analysis %>%
  dplyr::select(ID, age, SSI19_total_i, lifetime_stb, all_of(outcome_variables_predict)) %>%
  mutate(SSI19_i_z = scale(SSI19_total_i),
         stb = ifelse(lifetime_stb==1, 1, 0)) %>%
  pivot_longer(cols = all_of(outcome_variables_predict))


predict_nest = predict_long %>%
  group_by(name) %>%
  nest()


predict_si_z_models = predict_nest %>%
  mutate(model = purrr::map(data, ~glmmTMB(data = ., value ~ SSI19_i_z + age + (1|ID), 
                                           family = binomial(link = 'logit'))),
         coef = purrr::map(model, ~broom.mixed::tidy(., conf.int=TRUE))
  )

predict_stb_models = predict_nest %>%
  mutate(model = purrr::map(data, ~glmmTMB(data = ., value ~ stb + age + (1|ID), 
                                           family = binomial(link = 'logit'))),
         coef = purrr::map(model, ~broom.mixed::tidy(., conf.int=TRUE, exponentiate=TRUE))
  )


predict_si_z_coef = predict_si_z_models %>% unnest(coef) %>%
  dplyr::select(-model, -data) %>%
  dplyr::filter(term == 'SSI19_i_z')

predict_stb_or = predict_stb_models %>% unnest(coef) %>%
  dplyr::select(-model, -data) %>%
  dplyr::filter(term == 'stb')

summary(predict_stb_models$model[[2]])
```

```{r}
save(predict_si_z_models, predict_stb_models, file = '../model_outputs_step2/nobootstrap_outputs_gpt_vs_lexicon_predict.rda')
```


```{r}
predict_si_z_coef <- mutate(predict_si_z_coef, 
                      name_recode = dplyr::recode(name,
                                                  flag_bin = 'Flagged By Lexicon',
                                                  gpt_label = 'Lexicon + GPT4'),
                      lex = case_when(name=='flag_bin' ~ 'Flagged By Lexicon', 
                                      name == 'gpt_label' ~ 'Flagged by Lexicon + GPT',
                                      TRUE ~ 'Flagged By Lexicon\n+ Human Coding'))

predict_stb_or <- mutate(predict_stb_or, 
                      name_recode = dplyr::recode(name,
                                                  flag_bin = 'Flagged By Lexicon',
                                                  gpt_label = 'Lexicon + GPT4'),
                      lex = case_when(name=='flag_bin' ~ 'Flagged By Lexicon', 
                                      name == 'gpt_label' ~ 'Flagged by Lexicon + GPT',
                                      TRUE ~ 'Flagged By Lexicon\n+ Human Coding'))

predict_stb_or %>% dplyr::select(name, estimate, conf.low, conf.high)
predict_si_z_coef %>% dplyr::select(name, estimate, conf.low, conf.high)

```


# Combine non-bootstrapped analyses for figure 
```{r}

combined_stb_or = rbind(predict_stb_or %>% mutate(cohort = 'PREDICT'), 
                        maps_stb_or %>% mutate(cohort = 'MAPS')) %>%
  dplyr::filter(name %in% c('flag_bin', 'gpt_label', 'gpt')) %>%
  dplyr::mutate(
                plot_label = case_when(
                  name_recode == 'Flagged By Lexicon' ~ "Youth Suicide Lexicon Alone",
                  name_recode == 'Lexicon + GPT4' ~ 'Two-Stage Approach\nYouth Suicide Lexicon + GPT-4o mini'
                )
                )

combined_si_or = rbind(predict_si_z_coef %>% mutate(cohort = 'PREDICT'), 
                        maps_si_z_coef %>% mutate(cohort = 'MAPS')) %>%
  dplyr::filter(name %in% c('flag_bin', 'gpt_label', 'gpt')) %>%
  dplyr::mutate(
                plot_label = case_when(
                  name_recode == 'Flagged By Lexicon' ~ "Youth Suicide Lexicon Alone",
                  name_recode == 'Lexicon + GPT4' ~ 'Two-Stage Approach\nYouth Suicide Lexicon + GPT-4o mini'
                ),
                or = exp(estimate),
                or.conf.low = exp(conf.low),
                or.conf.high = exp(conf.high))


combined_stb_or_plot = ggplot(combined_stb_or, aes(x = plot_label, y = estimate, color = cohort)) +
  geom_hline(yintercept = 1, lty = 2) +
  geom_point(position = position_dodge(0.2), size = 2) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0, 
                position = position_dodge(0.2), lwd = 1) +
  coord_flip() +
  theme_bw() +
  labs(y = 'STB > Psychiatric Control\nOdds Ratio', x=NULL, color = NULL, title = 'A') +
  scale_y_log10() +
  theme(legend.position = 'none',
        text = element_text(face='bold')) +
  scale_color_manual(values = maps_predict_colors)

combined_si_or_plot = ggplot(combined_si_or, aes(x = plot_label, y = or, color = cohort)) +
  geom_hline(yintercept = 1, lty = 2) +
  geom_point(position = position_dodge(0.2), size = 2) + 
  geom_errorbar(aes(ymin = or.conf.low, ymax = or.conf.high), width = 0, 
                position = position_dodge(0.2), lwd = 1) +
  coord_flip() +
  theme_bw() +
  labs(y = 'Association with Self-Report Baseline Suicidal Ideation\nOdds Ratio', x=NULL, color = 'Cohort', title = 'B') +
  scale_y_log10() +
  theme(legend.position = 'bottom', 
        text = element_text(face='bold')) +
  scale_color_manual(values = maps_predict_colors)



fig6_twostage = cowplot::plot_grid(combined_stb_or_plot, combined_si_or_plot, nrow = 2, axis = 'v', align = 'lr')

cowplot::save_plot(fig6_twostage, file = '../figures/supplemental/rev1_added/lexicon_vs_two_stage.png',
                   base_width = 7, base_height = 6)
```


# PREDICT bootstrapping 
```{r}
n_iter = 100

boot_output = data.frame(iter = 0)

start_time = Sys.time()
for (i in 1:n_iter){
  #print(i)
  
  # only run if not already run for that iteration
  existing_outputs = dplyr::filter(boot_output, iter == i)
  if (nrow(existing_outputs) != 0){
    next
  }else{
   print(c('Boostrap iter', i))
  }
  
  boot_tmp=one_bootstrap_gpt(seed=i, df = predict_for_analysis %>% dplyr::select(SSI19_i=SSI19_total_i, everything()))
  if(i == 1){
    boot_output = boot_tmp
    }
  else{
      boot_output = rbind(boot_output, boot_tmp)
  }
  end_time = Sys.time()
  print(end_time - start_time)
  time_elapsed = end_time - start_time
  save(boot_output, time_elapsed, file = '../model_outputs_step2/bootstrap_outputs_gpt_vs_lexicon_predict.rda')
}

```