---
title: "Results of Lexicon+LLM vs Lexicon Alone Bootstrapping Analyses"
author: "Paul Alexander Bloom"
date: "2025-05-13"
output: html_document
---


To compare whether lexicon codings alone vs human coding (e.g., true positives) are more strongly associated with STB history/SI
Bootstrap, run models, compare odds ratios for each bootstrap iteration

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
library(glmmTMB)
library(emmeans)
library(lubridate)
library(ggplot2)
library(ggtext)
library(broom.mixed)
source('helper_functions.R')
options(scipen = 999)
```
# MAPS


```{r}
load('../model_outputs_step2/bootstrap_outputs_gpt_vs_lexicon_maps.rda')

```

# Summarize bootstrap outputs
```{r}
stb_compare_maps = boot_output %>% dplyr::filter(term == 'lifetime_stb')
si_compare_maps = boot_output %>% dplyr::filter(term == 'SSI19_i')


stb_compare_maps = stb_compare_maps %>%
  pivot_wider(id_cols = 'iter', names_from = 'coding', values_from = 'estimate') %>%
  mutate(ratio= gpt / lexicon,
         above_1 = ratio > 1)

si_compare_maps = si_compare_maps %>%
  pivot_wider(id_cols = 'iter', names_from = 'coding', values_from = 'estimate') %>%
  mutate(ratio= gpt / lexicon,
         above_1 = ratio > 1)

```

stb odds ratio comparison
```{r}
sum(stb_compare_maps$above_1 / nrow(stb_compare_maps))
mean(stb_compare_maps$ratio)

quantile(stb_compare_maps$ratio, c(.025, .975))
```

si odds ratio comparison
```{r}

sum(si_compare_maps$above_1 / nrow(si_compare_maps))
mean(si_compare_maps$ratio)

quantile(si_compare_maps$ratio, c(.025, .975))

```

# PREDICT

```{r}
load('../model_outputs_step2/bootstrap_outputs_gpt_vs_lexicon_predict.rda')

```

# Summarize bootstrap outputs
```{r}
stb_compare_predict = boot_output %>% dplyr::filter(term == 'lifetime_stb')
si_compare_predict = boot_output %>% dplyr::filter(term == 'SSI19_i')


stb_compare_predict = stb_compare_predict %>%
  pivot_wider(id_cols = 'iter', names_from = 'coding', values_from = 'estimate') %>%
  mutate(ratio= gpt / lexicon,
         above_1 = ratio > 1)

si_compare_predict = si_compare_predict %>%
  pivot_wider(id_cols = 'iter', names_from = 'coding', values_from = 'estimate') %>%
  mutate(ratio= gpt / lexicon,
         above_1 = ratio > 1)

```

stb odds ratio comparison
```{r}
sum(stb_compare_predict$above_1 / nrow(stb_compare_predict))
mean(stb_compare_predict$ratio)

quantile(stb_compare_predict$ratio, c(.025, .975))
```

si odds ratio comparison
```{r}

sum(si_compare_predict$above_1 / nrow(si_compare_predict))
mean(si_compare_predict$ratio)

quantile(si_compare_predict$ratio, c(.025, .975))

```

